An efficient composition of bidirectional programs by tupling and lazy updates

### 2020-02-21 paper/5.experiments.tex
small fix

Note that this result concerns BX programs that uses many compositions. If the number of compositions is small, the original $put$ without any memoization will be fastest because of the overhead for memoization ($put_m$) and the overhead for keeping complements in closures ($xpg$).

>>>>

Note that this result concerns BX programs that use many compositions. If the number of compositions is small, the original $put$ without memoization will be fastest because of the overhead for memoization ($put_m$) and the overhead for keeping complements in closures ($xpg$).

### 2020-02-21 paper/main.tex
fix typo
small fix

\subsubsection*{Acknowledgement}
We thank the anonymous reviewers for valuable comments and suggestions. This work has been partially supported by JSPS KAKENHI Grant Number JP17H06099.

>>>>

\subsubsection*{Acknowledgment}
We thank the anonymous reviewers for valuable comments and suggestions. This work has been partially supported by JSPS KAKENHI Grant Number JP17H06099, and ROIS NII Open Collaborative Research 2018.
